Landscape composition and beneficial insects

### 2020-06-23 manuscript/manuscript_outline.Rmd
Added to refs

* The predatory ground beetle _Pterostichus melanarius_ responded to landscape composition, primarily to different crop types (Table \@ref(tab:sumTab),\@ref(tab:PteMelSmooth))
  + Of the non-crop land categories, grassland and wetland cover acted as a late-season sink, suggesting that _P. melanarius_ may migrate into it at the end of the summer
  + Other studies have found similar results, suggesting that untilled land is important off-field habitat for carabids [@desender1988; @fournier2002; but see @hatten2007]
 + In particular, @purtauf2005 found that carabid density increased with proportion of nearby grasslands; our finding of grassland/wetland as late-season sink may represent _P. melanarius_ moving to overwintering habitat at the end of the season
 + However, _P. melanarius_ is also found in a wide variety of habitats, and tends to prefer agricultural fields [@larsen2003], which our models also demonstrated
 + We found that canola and pulse crops acted as early- and mid-season sources of _P. melanarius_ 
 + The roles that carabids play in pulse crops is not well-studied, but carabids are known predators of pea-leaf weevils (_Sitona lineatus_) on other Fabacea [@hamon1990]
 + Alternatively, _P. melanarius_ is known to predate upon other carabid predators of _S. lineatus_, such as _Bembidion quadrimaculatum_ [@vankosky2011]
 + Either way this suggests that pulses may represent a potential food resource for _P. melanarius_, at least earlier in the season

@@

* These patterns indicate movement between landscape features, but since we did not directly observe arthropod movement between features, future studies should examine this
  + Mark-recapture studies, monitoring movement patterns (e.g. radio tags), or two-sided traps could be useful
  + Should also be linked to ecosystem services (e.g. predation on bait insects or weed seeds)

>>>>

* The predatory ground beetle _Pterostichus melanarius_ responded to landscape composition, primarily to different crop types (Table \@ref(tab:sumTab),\@ref(tab:PteMelSmooth))
  + Of the non-crop land categories, grassland and wetland cover acted as a late-season sink, suggesting that _P. melanarius_ may migrate into it at the end of the summer
  + Other studies have found similar results, suggesting that untilled land is important off-field habitat for carabids [@desender1988; @fournier2002; but see @hatten2007]
 + In particular, @purtauf2005 found that carabid density increased with proportion of nearby grasslands; our finding of grassland/wetland as late-season sink may represent _P. melanarius_ moving to overwintering habitat at the end of the season
 + However, _P. melanarius_ is also found in a wide variety of habitats, and tends to prefer agricultural fields [@larsen2003], which our models also demonstrated
 + We found that canola and pulse crops acted as early- and mid-season sources of _P. melanarius_ 
 + The roles that carabids play in pulse crops is not well-studied, but carabids are predators of pea-leaf weevils (_Sitona lineatus_) on other Fabaceae [@hamon1990]
 + Alternatively, _P. melanarius_ is known to predate upon other carabid predators of _S. lineatus_, such as _Bembidion quadrimaculatum_ [@vankosky2011]
 + Either way this suggests that pulses may represent a potential food resource for _P. melanarius_, at least earlier in the season
 + Surprisingly, flax acted as a local and landscape level sink, suggesting that it may

@@

* These patterns indicate movement between landscape features, but since we did not directly observe arthropod movement between features, future studies should examine this
  + Some land cover classes were strongly concurved (canola and cereal, wetland and grassland) with each other, we removed or combined them, meaning that we could not consider the influence of the categories independently 
  + Mark-recapture studies, monitoring movement patterns (e.g. radio tags), or two-sided traps could be useful
  + Should also be linked to ecosystem services (e.g. predation on bait insects or weed seeds)
